\vspace{1.0cm} \Large \bf Integrating influenza antigenic dynamics with molecular evolution

### 2013-03-09 flux.tex
Fix author contributions.

AR, MAS, TB and PL conceived the study.
TB, GD, VG, JWM, AJH, CAR, DJS and AR gathered antigenic and genetic data.
AR, MAS, TB and PL designed statistical phylogenetic procedures.
TB performed the analysis.
TB, MAS, AR, JWM, AJH wrote the paper.

>>>>

AR, MAS, TB conceived the study.
AR, MAS, TB, DJS, PL designed the antigenic model.
TB, GD, VG, JWM, AJH, CAR, DJS and AR gathered antigenic and genetic data.
AR, MAS, TB and PL implemented statistical phylogenetic procedures.
TB performed the analysis.
TB, AR, DJS, JWM, PL, CAR, AJH, GD, MAS interpreted the results.
TB, MAS, AR, JWM, AJH wrote the paper.
